---
title: "Simulation_data_generate"
output: pdf_document
---

1. Choose different cox distributions to generate data
2. Choose different beta
3. Create functions to simplify codes
4. Visualization
  4.1 KM-curve vs. fitted curve
  4.2 beta ~ MSE with different parameters to generate data
  4.3 ...
5. discussion: description, pros and cons
...
```{r setup, echo = FALSE, warnings = FALSE}
library(tidyverse)
library(survival)
library(pracma)
library(ggplot2)
library(survminer)
library(flexsurv)
library(patchwork)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%",
  warning = FALSE
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Generate survival data
```{r}
set.seed(666)

# Generate survival data
genn_dat <- function(n, lambda, beta, gamma, alpha, dist) {
  # Generate key for each observation
  id <- seq(1:n)
  
  # Predictor X (treatment = 1; control = 0)
  x <- rbinom(n, size = 1, prob = 0.5)
  
  ## --- Generate Survival Time T --- 
  U <- runif(n)
  # Use exponential distribution
  expo <- function(U, lambda, x, beta) {
    -log(U) / (lambda * exp(x * beta))
  }
  
  # Use weibull distribution
  weibull <- function(U, lambda, x, gamma, beta) {
    (-log(U) / (lambda * exp(x * beta))) ^ (1 / gamma)
  }
  
  # --- To be modified (add cox function) ---
  # Use 'Cox' distribution -- gompertz
  gompertz <- function(U, alpha, lambda, x, beta) {
    (1 / alpha) * (1 - alpha * log(U) / (lambda * exp(x * beta)))
  }
  
  # Select different baseline functions
  if (dist == "expo") {
    surv_t <- expo(U, lambda, x, beta)}
  else if (dist == "weibull") {
    surv_t <- weibull(U, lambda, x, gamma, beta)
  }
  else {
    surv_t <- gompertz(U, alpha, lambda, x, beta)
  }
  
  return(
    df = data.frame(
      id = id,
      treatment = x,
      time = surv_t
    )
  )
}
```


## Fit models
```{r}
# Set the truth (beta = 0.5)

# --- MODIFY sample size or beta ---
# Generate data from exponential
set.seed(666)
dat <- genn_dat(n = 10000, lambda = 2, beta = 0.5, gamma = 3, dist = "weibull")

fit_km <- survfit(Surv(dat$time) ~ dat$treatment, data = dat)
# Fit exponential model
fit_expo <- flexsurvreg(Surv(dat$time) ~ as.factor(dat$treatment), dist = "exponential", data = dat)
- fit_expo$coefficients[-1]

# Weibull
fit_weibull <- survreg(Surv(dat$time) ~ dat$treatment, dist = "weibull")
- fit_weibull$coefficients[-1] / fit_weibull$scale

# `Cox` -- gompertz
fit_cox <- coxph(Surv(dat$time) ~ dat$treatment)
summary(fit_cox)
```


## Visualization(beta = 0.5)

### 1. data-exponential(lambda = 2)

```{r}
## Generate Data
set.seed(666)
dat_1 <- genn_dat(n = 100, lambda = 2, beta = 0.5, dist = "expo")
s_1 <- with(dat_1, Surv(time))

## Exponential
fit_expo_1 = flexsurvreg(s_1 ~ as.factor(treatment), dist = 'exponential', data = dat_1)
plot(fit_expo_1, col = c('red', 'blue'), main = "Exponential proportional-hazards model")
legend("topright", legend = c('Treatment', 'Control'), col = c('red', 'blue'), lty = 1, cex = 0.8)

## Weibull
fit_wei_1 = flexsurvreg(s_1 ~ as.factor(treatment), dist = 'weibull', data = dat_1)
plot(fit_wei_1, col = c('red', 'blue'), main = "Weibull proportional-hazards model")
legend("topright", legend = c('Treatment', 'Control'), col = c('red', 'blue'), lty = 1, cex = 0.8)

## Cox
fit_km_1 = survfit(s_1 ~ treatment, data = dat_1)
plot(fit_km_1, conf.int = F, main = "Cox proportional-hazards model")
fit_cox_1 = coxph(s_1 ~ as.factor(treatment), data = dat_1)
lines(survfit(fit_cox_1, newdata = data.frame(treatment = 0)), col = "blue", conf.int = F)
lines(survfit(fit_cox_1, newdata = data.frame(treatment = 1)), col = "red", conf.int = F)
legend("topright", legend = c('Treatment', 'Control'), col = c('red', 'blue'), lty = 1, cex = 0.8)
```

### 2. data-weibull(lambda = 2, gamma = 1)

```{r}
## Generate Data
set.seed(666)
dat_2 <- genn_dat(n = 100, lambda = 2, beta = 0.5, gamma = 1, dist = "weibull")
s_2 = with(dat_2, Surv(time))

## Exponential
fit_expo_2 = flexsurvreg(s_2 ~ as.factor(treatment), dist = 'exponential', data = dat_2)
plot(fit_expo_2, col = c('red', 'blue'), main = "Exponential proportional-hazards model")
legend("topright", legend = c('Treatment', 'Control'), col = c('red', 'blue'), lty = 1, cex = 0.8)

## Weibull
fit_wei_2 = flexsurvreg(s_2 ~ as.factor(treatment), dist = 'weibull', data = dat_2)
plot(fit_wei_2, col = c('red', 'blue'), main = "Weibull proportional-hazards model")
legend("topright", legend = c('Treatment', 'Control'), col = c('red', 'blue'), lty = 1, cex = 0.8)

## Cox
fit_km_2 = survfit(s_2 ~ treatment, data = dat_2)
plot(fit_km_2, conf.int = F, main = "Cox proportional-hazards model")
fit_cox_2 = coxph(s_2 ~ as.factor(treatment), data = dat_2)
lines(survfit(fit_cox_2, newdata = data.frame(treatment = 0)), col = "blue", conf.int = F)
lines(survfit(fit_cox_2, newdata = data.frame(treatment = 1)), col = "red", conf.int = F)
legend("topright", legend = c('Treatment', 'Control'), col = c('red', 'blue'), lty = 1, cex = 0.8)
```

### 3. data-gompertz(alpha = 2, lambda = 2)

```{r}
## Generate Data
set.seed(666)
dat_3 <- genn_dat(n = 100, lambda = 2, beta = 0.5, alpha = 2, dist = "gompertz")
s_3 = with(dat_3, Surv(time))

## Exponential
fit_expo_3 = flexsurvreg(s_3 ~ as.factor(treatment), dist = 'exponential', data = dat_3)
plot(fit_expo_3, col = c('red', 'blue'), main = "Exponential proportional-hazards model")
legend("topright", legend = c('Treatment', 'Control'), col = c('red', 'blue'), lty = 1, cex = 0.8)

## Weibull
fit_wei_3 = flexsurvreg(s_3 ~ as.factor(treatment), dist = 'weibull', data = dat_3)
plot(fit_wei_3, col = c('red', 'blue'), main = "Weibull proportional-hazards model")
legend("topright", legend = c('Treatment', 'Control'), col = c('red', 'blue'), lty = 1, cex = 0.8)

## Cox
fit_km = survfit(s_3 ~ treatment, data = dat_3)
plot(fit_km, conf.int = F, main = "Cox proportional-hazards model")
fit_cox_3 = coxph(s_3 ~ as.factor(treatment), data = dat_3)
lines(survfit(fit_cox_3, newdata = data.frame(treatment = 0)), col = "blue", conf.int = F)
lines(survfit(fit_cox_3, newdata = data.frame(treatment = 1)), col = "red", conf.int = F)
legend("topright", legend = c('Treatment', 'Control'), col = c('red', 'blue'), lty = 1, cex = 0.8)

```

